The title

### 2018-04-26 writeup.Rmd
more intro

---
title             : "The title"
shorttitle        : "Title"
author:

  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Second Author"
    affiliation   : "1"
  - name          : "Third Author"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Stanford University"
author_note: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.

keywords          : "keywords"
wordcount         : "X"
bibliography      : ["r-references.bib"]
figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no
class             : "man"
output            : papaja::apa6_pdf
editor_options: 
  chunk_output_type: console
---

```{r load_packages, include = FALSE}
library(grid)
library(gtable)
library(papaja)
library(tidyverse)
library(magrittr)
library(readr)
library(png)
library(jpeg)
library(lme4)
library(ggthemes)
library(forcats)
library(brms)
```

@@

@@

# high definition only considers the highest point on the scale as "literal"
pragmatic_trials$high<-1
pragmatic_trials[pragmatic_trials$response=="Right"]$high <-0

# low definition only considers the lowers point on the scale as implicature 
pragmatic_trials$low<-0
pragmatic_trials[pragmatic_trials$response=="Wrong"]$low <-1

@@

summary(implicature_analysis)

implicature_analysis_b <- brm(implicature ~ definition * response_type + trial_type + (1+response_type|trial_type) + (1|participant), family="binomial", data=implicature_rate)
```

>>>>

---
title             : "The effect of linking assumptions and number of response options on inferred scalar implicature rate"
shorttitle        : "Linking assumptions and implicature rate"
author:

  - name          : "Masoud Jasbi"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Brandon Waldon"
    affiliation   : "1"
  - name          : "Judith Degen"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Stanford University"
author_note: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.

keywords          : "scalar implicature; methodology; linking assumption; experimental pragmatics; truth-value judgment task"
wordcount         : "X"
bibliography      : ["r-references.bib"]
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no
class             : "man"
output            : papaja::apa6_pdf
editor_options: 
  chunk_output_type: console
---

```{r load_packages, include = FALSE}
library(grid)
library(gtable)
library(papaja)
library(tidyverse)
library(magrittr)
library(readr)
library(png)
library(jpeg)
library(lme4)
library(ggthemes)
library(forcats)
# library(brms)
theme_set(theme_bw(18))
```

@@

The past 15 years have seen the rise and development of a bustling and exciting new field at the intersection of linguistics, psychology, and philosophy: *experimental pragmatics* [@bott2004;@Breheny2006;@DegenTanenhaus2015;@Grodner2010;@huang2009;@Geurts2009;@noveck2008] **XXX ADD MORE**. Experimental pragmatics is devoted to experimentally testing theories of how language is used in context. How do listeners draw inferences about the -- often underspecified -- linguistic signal they receive from speakers? How do speakers choose between the many utterance alternatives they have at their disposal?

The most prominently studied phenomenon in experimental pragmatics is undoubtedly *scalar implicature*. Scalar implicatures arise in virtue of a speaker producing the weaker of two ordered scalemates [@grice1975; hornXXX; @hirschberg1985; @Geurts2010]. Examples are provided in (1) and (2).

1. 
  a. *Utterance:* Some of her pets are cats.
  b. *Implicature:* Some, but not all, of her pets are cats.
  c. *Scale:* <all, some>

2. 
  a. *Utterance:* She owns a cat or a dog.
  b. *Implicature:* She owns a cat or a dog, but not both.
  c. *Scale:* <and, or>

A listener, upon observing the utterances in (1a) and (2a), typically infers that the speaker intended to convey the meanings in (1b) and (2b), respectively. Since @grice1975, the agreed-upon abstract rationalization the listener could give for their inference goes something like this: if the speaker knows whether the stronger alternative (e.g., *All of her pets are cats.*) is true, then if it is, they should have produced it. They chose not to. I believe the speaker knows whether the stronger alternative is true. Hence, it must not be true.

CONTINUE HERE: motivation for examining implicature rate assumptions:

* surging interest in differences in implicature rates (eg van tiel, dgen tanenhaus)
* implicature rates serve as basis for claims about online processing (bott & noveck, degen tanenhaus)
* implicature rates serve as basis for claims about children (bishop katsos, barner, frank)

* add @deneys2007
* @demarneffetonhauser for investigations of scalar adjectives, and @vantiel

```{r linkvisualization, fig.env = "figure", fig.align='center', fig.width=5, set.cap.width=T, num.cols.cap=1,fig.cap = "Strong and weak link from response options to researcher inference about scalar implicature rate, exemplified for the disjunctive utterance when the conjunction is true."}
link_img <- png::readPNG("writeup_files/figures/link-visualization.png")
grid::grid.raster(link_img)
```

@@

# high definition only considers the highest point on the scale as "literal"
pragmatic_trials$high<-1
pragmatic_trials[pragmatic_trials$response=="Right",]$high <-0

# low definition only considers the lowers point on the scale as implicature 
pragmatic_trials$low<-0
pragmatic_trials[pragmatic_trials$response=="Wrong",]$low <-1

@@

summary(implicature_analysis_a)

# implicature_analysis_b <- brm(implicature ~ definition * response_type + trial_type + (1+response_type|trial_type) + (1|participant), family="binomial", data=implicature_rate)
```
